\begin{flushleft}
\begin{thebibliography}{00} %60
\bibitem{b1} AAC Clyde Space. \textbf{Datasheet: Kryten-M3}. Disponível em $<$https://www.aac-clyde.space/wp-content/uploads/2021/10/AAC\_DataSheet\_Kryten.pdf$>$.  Acesso em: 07 jun. 2024.

\bibitem{b36} \textbf{A3G4250D Gyroscope Datasheet}. Disponível em: $<$\url{https://www.st.com/content/ccc/resource/technical/document/datasheet/5c/f1/a4/70/1b/fa/40/d2/DM00047823.pdf/files/DM00047823.pdf/jcr:content/translations/en.DM00047823.pdf}$>$. Acesso em: 27 out. 2024. 

\bibitem{b21} \textbf{AN-600: Understanding Latch-Up in Advanced CMOS Logic}. [s.l: s.n.]. Disponível em: $<$https://large.stanford.edu/courses/2015/ph241/clark2/docs/AN-600.pdf$>$. Acesso em: 26 out. 2024.

\bibitem{b48} BARLES, A. et al. \textbf{Mission ORCA: Orbit refinement for collision avoidance}. Advances in Astronautics Science and Technology, v. 5, n. 2, p. 149–165, 2022.

%\bibitem{b57} BOING, M. \textbf{Técnicas de mitigação de efeitos da radiação e sua aplicação no projeto de uma arquitetura de hardware para uso em satélites}. Florianópolis, SC: UFSC, 19 de julho de 2024.

\bibitem{b56} BOUKHOBZA, J.; OLIVIER, P. \textbf{Emerging Non-volatile Memories}. Em: Flash Memory Integration. [s.l.] Elsevier, 2017. p. 203–224.

\bibitem{b40} CADENCE PCB SOLUTIONS. \textbf{Zener diode applications: Circuit protection}. Disponível em: <https://resources.pcb.cadence.com/blog/2023-zener-diode-applications-circuit-protection>. Acesso em: 28 out. 2024

\bibitem{b13} CARMO, T. A.; MOREIRA , J. Q.; MANEA, S. \textbf{Análise de blindagem à radiação “TID” e “SEU” em memória do tipo SRAM em orbita LEO (Low Earth Orbit)}. 12° Workshop em Engenharia e Tecnologia Espaciais, 6 nov. 2021.

\bibitem{b49} CAMPS, A. et al. \textbf{Fsscat, the 2017 Copernicus masters’ “Esa sentinel small satellite challenge” winner: A federated polar and soil moisture tandem mission based on 6U cubesats}. IGARSS 2018 - 2018 IEEE International Geoscience and Remote Sensing Symposium. Anais...IEEE, 2018.

\bibitem{b2} CAPPELLETTI, C.; BATTISTINI, S.; MALPHRUS, B. \textbf{Cubesat Handbook: From Mission Design to Operations}. Editora Elsevier, 2021.

\bibitem{b58} \textit{CubeSat101: Basic Concepts and Processes for First-Time CubeSat Developers}. [S.l.: s.n.], 2017. Disponível em $<$https://www.nasa.gov/wp-content/uploads/2017/03/nasa\_csli\_cubesat\_101\_508.pdf?emrc=05d3e2$>$. Acesso em 28 out. 2024.

\bibitem{b15} \textbf{CUBESAT Design Specification}. [S.l.: s.n.], 2022. Disponível em $<$https://www.cubesat.org/cubesatinfo$>$. Acesso em: 25 out. 2024.

\bibitem{b22} \textbf{CY15B104QN FRAM Datasheet}. Disponível em: $<$\url{https://www.infineon.com/dgdl/Infineon-CY15B104QN\_CY15V104QN\_Excelon(TM)\_LP\_4-Mbit\_(512K\_X\_8)\_Serial\_(SPI)\_F-RAM-DataSheet-v12\_00-EN.pdf?fileId=8ac78c8c7d0d8da4017d0ee7709b704a\&utm\_source=cypress\&utm\_medium=referral\&utm\_campaign=202110\_globe\_en\_all\_integr}$>$. Acesso em: 27 out. 2024.

\bibitem{b47} \textbf{DS191 - Zynq-7000 SoC (Z-7030, Z-7035, Z-7045, and Z-7100): DC and AC Switching Characteristics}. 2018. Disponível em $<$https://docs.amd.com/v/u/en-US/ds191-XC7Z030-XC7Z045-data-sheet$>$. Acesso em: 29 out. 2024.

\bibitem{b14} ECSS. \textbf{ECSS-Q-ST-60C Rev.3 – Electrical, electronic and electromechanical (EEE) components (12 May 2022)}. Disponível em: $<$https://ecss.nl/standard/ecss-q-st-60c-rev-3-electrical-electronic-and-electromechanical-eee-components-2-may-2022/$>$. Acesso em: 6 out. 2024.

\bibitem{b57} ECSS. \textbf{ECSS-E-ST-10-04C - Space Environment}. The Netherlands: [s.n.], 2008.

\bibitem{b20} GERARDIN, S.; PACCAGNELLA, A. \textbf{Present and future non-volatile memories for space}. IEEE transactions on nuclear science, 2010.

\bibitem{b3} GEORGE, A. D.; WILSON, C. M. \textbf{Onboard processing with hybrid and reconfigurable computing on small satellites}. Proceedings of the IEEE. Institute of Electrical and Electronics Engineers, 2018.

\bibitem{b4} \textbf{Gomspace NanoMind A3200 Datasheet}. Disponível em $<$https://gomspace.com/UserFiles/Subsystems/datasheet/gs-ds-nanomind-a3200\_1006901-117.pdf$>$. Acesso em: 07 jun. 2024.

\bibitem{b5} \textbf{Gomspace NanoMind HP MK3 Datasheet}. Disponível em $<$https://gomspace.com/UserFiles/Subsystems/datasheet/gs-ds-NanoMind\_HP\_MK3.pdf$>$. Acesso em: 07 jun. 2024.

\bibitem{b51} \textbf{Gomspace Nanomind Z7000 Datasheet}. 2019. Disponível em: $<$https://gomspace.com/UserFiles/Subsystems/datasheet/gs-ds-nanomind-z7000-15.pdf$>$. Acesso em: 30 oct. 2024.

\bibitem{b34} \textbf{INA180A2IDBVR Current Sense Datasheet}. Disponível em: $<$\url{https://www.ti.com/lit/ds/symlink/ina180.pdf?HQS=dis-dk-null-digikeymode-dsf-pf-null-wwe\&ts=1727202734954\&ref\_url=https\%253A\%252F\%252Fwww.ti.com\%252Fgeneral\%252Fdocs\%252Fsuppproductinfo.tsp\%253FdistId\%253D10\%2526gotoUrl\%253Dhttps\%253A\%252F\%252Fwww.ti.com\%252Flit\%252Fgpn\%252Fina180}$>$. Acesso em: 27 out. 2024. 

\bibitem{b6} \textbf{ISIS Space On Board Computer}. Disponível em $<$https://www.isispace.nl/product/on-board-computer/$>$. Acesso em: 07 jun. 2024.

\bibitem{b19} JEDEC. \textbf{Double Data Rate (DDR) SDRAM Standard}. 2008. Disponível em: $<$https://www.jedec.org/standards-documents/docs/jesd-79f$>$. Acesso em: 26 out. 2024.

\bibitem{b10} JUNQUEIRA, B. C.; MANEA, S.\textbf{Utilização de COTS em nano satélites}. Brazilian Journal of Development, v. 6, n. 1, p. 1476-1490, 2020.

\bibitem{b16} KADI, M. A. et al. \textbf{Dynamic and partial reconfiguration of Zynq 7000 under Linux}. 2013 International Conference on Reconfigurable Computing and FPGAs (ReConFig). Anais...IEEE, 2013.

\bibitem{b18} KLEHN, B.; BROX, M. A. \textbf{Comparison of current SDRAM types: SDR, DDR, and RDRAM}. Advances in radio science, v. 1, p. 265–271, 2003.

\bibitem{b59} LABEL, K. A. \textbf{Radiation Effects on Electronics 101: Simple Concepts and New Challenges}. NEPP Webex Presentation, 2004.

\bibitem{b54} LOFFLER, T. et al. \textbf{Research and Observation in Medium Earth Orbit (ROMEO) with a cost-effective microsatellite platform}. 72nd International Astronautical Congress (IAC), Dubai, United Arab Emirates. 2021. 

\bibitem{b12} \textbf{Low earth orbit}. Disponível em: $<$https://www.esa.int/ESA\_Multimedia/Images/2020/03/Low\_Earth\_orbit$>$. Acesso em: 6 out. 2024.

\bibitem{b27} \textbf{LTC2991IMS\#TRPBF Voltage, Current and Temperature Monitor Datasheet}. Disponível em: $<$https://www.analog.com/media/en/technical-documentation/data-sheets/2991ff.pdf$>$. Acesso em: 27 out. 2024. 

\bibitem{b37} \textbf{LTC4361 Overcurrent Protection Controller Datasheet}. 2018. Disponível em: $<$https://www.analog.com/media/en/technical-documentation/data-sheets/LTC4361-1-4361-2.pdf$>$. Acesso em: 27 out. 2024. 

\bibitem{b11} MAYANBARI, Masood; KASESAZ, Yaser. \textbf{Design and analyse space radiation shielding for a nanosatellite in Low Earth Orbit (LEO)}. In: Proceedings of 5th International Conference on Recent Advances in Space Technologies-RAST2011. IEEE, 2011. p. 489-493.

\bibitem{b42} MAK, B. \textbf{Basics of Load Switches}. 2018. Disponível em: <https://www.ti.com/lit/an/slva652a/slva652a.pdf?ts=1730079105016>. Acesso em: 28 out. 2024.

\bibitem{b8} MARCELINO, G. M. et al. \textbf{A critical embedded system challenge: The FloripaSat-1 mission}. IEEE Latin America Transactions, 2020.

\bibitem{b9} MARCELINO, G. M. et al. \textbf{FloripaSat-2: An Open-Source Platform for CubeSats}. IEEE embedded systems letters, 2024.

\bibitem{60} MATTOS, A. M. P. \textbf{HARSH ENVIRONMENT CUBESAT PAYLOAD}. 2020. Disponível em $<$https://github.com/andrempmattos/harsh-payload$>$. Acesso em: 06 nov. 2024.

\bibitem{b35} \textbf{MMC5983MA Magnetometer Datasheet}. Disponível em: $<$\url{https://mm.digikey.com/Volume0/opasdata/d220001/medias/docus/333/MMC5983MA\_RevA\_4-3-19.pdf}$>$. Acesso em: 27 out. 2024. 

\bibitem{b25} \textbf{MT25QL128ABB1ESE-0AUT Flash NOR Datasheet}. Disponível em: $<$https://www.micron.com/content/dam/micron/global/secure/products/data-sheet/nor-flash/serial-nor/mt25q/die-rev-b/mt25q-qlht-l-128-abb-xxt.pdf$>$. Acesso em: 27 out. 2024. 

\bibitem{b24} \textbf{MT29F1G01ABAFDSF-AAT:F Flash NAND Datasheet}. Disponível em: $<$https://www.micron.com/content/dam/micron/global/secure/products/data-sheet/nand-flash/70-series/m78a-1gb-spi-auto.pdf$>$. Acesso em: 27 out. 2024. 

\bibitem{b23} \textbf{MT41K256M8DA-125:K DDR3L Datasheet}. Disponível em: $<$https://www.micron.com/content/dam/micron/global/secure/products/data-sheet/dram/ddr3/2gb-1-35v-ddr3l.pdf$>$. Acesso em: 27 out. 2024. 

\bibitem{b7} Nano Avionics. \textbf{CubeSat On-Board Computer – Main Bus Unit SatBus 3C2}. Disponível em $<$https://nanoavionics.com/cubesat-components/cubesat-on-board-computer-main-bus-unit-satbus-3c2/$>$. Acesso em: 07 jun. 2024.

\bibitem{b13} \textbf{NASA Parts Selection List (NPSL)}. Disponível em: $<$https://nepp.nasa.gov/npsl/$>$. Acesso em: 6 out. 2024.

\bibitem{b55} \textbf{NASA Product Verification}. Disponível em: $<$https://www.nasa.gov/reference/5-3-product-verification/$>$. Acesso em: 30 out. 2024.

\bibitem{b53} PUTRA, A. C. A. Y.; WIJANTO, H.; EDWAR. \textbf{Design and implementation RTOS (real time operating system) as a nano satellite control for responding to space environmental conditions}. 2021 IEEE Asia Pacific Conference on Wireless and Mobile (APWiMob). Anais...IEEE, 2021.

\bibitem{b41} SARJEANT, W. \textbf{Capacitors}. IEEE transactions on electrical insulation, v. 25, n. 5, p. 861–922, 1990.

\bibitem{b39} SOH, W.-S. et al. \textbf{Filter design for suppression of noise coupling from PCB to DC power supply}. 2010 Asia-Pacific International Symposium on Electromagnetic Compatibility. Anais...IEEE, 2010.

\bibitem{b28} \textbf{TCA4311ADR I2C Buffer Datasheet}. Disponível em: $<$\url{https://www.ti.com/general/docs/suppproductinfo.tsp?distId=10\&gotoUrl=https\%3A\%2F\%2Fwww.ti.com\%2Flit\%2Fgpn\%2Ftca4311a}$>$. Acesso em: 27 out. 2024. 

\bibitem{b33} \textbf{TCAN330D CAN Transceiver Datasheet}. Disponível em: $<$\url{https://www.ti.com/lit/ds/symlink/tcan330.pdf?ts=1729084231140\&ref\_url=https\%253A\%252F\%252Fbr.mouser.com\%252F}$>$. Acesso em: 27 out. 2024. 

\bibitem{b29} \textbf{THVD1451DR RS-485 Transceiver Datasheet}. Disponível em: $<$\url{https://www.ti.com/lit/ds/symlink/thvd1410.pdf?HQS=dis-dk-null-digikeymode-dsf-pf-null-wwe\&ts=1722094226249\&ref\_url=https\%253A\%252F\%252Fwww.ti.com\%252Fgeneral\%252Fdocs\%252Fsuppproductinfo.tsp\%253FdistId\%253D10\%2526gotoUrl\%253Dhttps\%253A\%252F\%252Fwww.ti.com\%252Flit\%252Fgpn\%252Fthvd1410}$>$. Acesso em: 27 out. 2024. 

\bibitem{b30} \textbf{TPS22920YZPR Load Switch Datasheet}. 2016. Disponível em: $<$\url{https://www.ti.com/general/docs/suppproductinfo.tsp?distId=10\&gotoUrl=https\%3A\%2F\%2Fwww.ti.com\%2Flit\%2Fgpn\%2Ftps22920}$>$. Acesso em: 27 out. 2024. 

\bibitem{b26} \textbf{TPS3823-33QDBVRQ1 Watchdog Timer Datasheet}. Disponível em: $<$\url{https://www.ti.com/general/docs/suppproductinfo.tsp?distId=10\&gotoUrl=https\%3A\%2F\%2Fwww.ti.com\%2Flit\%2Fgpn\%2Ftps3828-q1}$>$. Acesso em: 27 out. 2024. 

\bibitem{b31} \textbf{TPS51200DRCR DC-DC Voltage Regulator Datasheet}. Disponível em: $<$\url{https://www.ti.com/general/docs/suppproductinfo.tsp?distId=10\&gotoUrl=https\%3A\%2F\%2Fwww.ti.com\%2Flit\%2Fgpn\%2Ftps51200}$>$. Acesso em: 27 out. 2024. 

\bibitem{b32} \textbf{TPS82085SILR DC-DC Voltage Regulator Datasheet}. 2019. Disponível em: $<$\url{https://www.ti.com/general/docs/suppproductinfo.tsp?distId=10\&gotoUrl=https\%3A\%2F\%2Fwww.ti.com\%2Flit\%2Fgpn\%2Ftps82085}$>$. Acesso em: 27 out. 2024. 

\bibitem{b44} \textbf{UG470 - 7 Series FPGAs Configuration User Guide}. 2023. Disponível em $<$https://docs.amd.com/v/u/en-US/ug470\_7Series\_Config$>$. Acesso em: 29 out. 2024.

\bibitem{b45} \textbf{UG480 - 7 Series FPGAs and Zynq-7000 SoC XADC Dual 12-Bit 1 MSPS Analog-to-Digital Converter User Guide}. 2022. Disponível em $<$https://docs.amd.com/r/en-US/ug480\_7Series\_XADC$>$. Acesso em: 29 out. 2024.

\bibitem{b38} \textbf{UG585 - Zynq 7000 SoC Technical Reference Manual - AMD technical information portal}. 2023. Disponível em: $<$https://docs.amd.com/r/en-US/ug585-zynq-7000-SoC-TRM/Zynq-7000-SoC-Technical-Reference-Manual$>$. Acesso em: 25 out. 2024.

\bibitem{b17} \textbf{UG865 - Zynq-7000 SoC Packaging and Pinout Product Specification - AMD technical information portal}. 2021. Disponível em: $<$https://docs.amd.com/v/u/en-US/ug865-Zynq-7000-Pkg-Pinout$>$. Acesso em: 25 out. 2024.

\bibitem{b46} \textbf{UG933 - Zynq-7000 SoC PCB Design Guide}. 2019. Disponível em $<$https://docs.amd.com/v/u/en-US/ug933-Zynq-7000-PCB$>$. Acesso em: 29 out. 2024.

\bibitem{b50} WEIDMANN, D. et al. \textbf{Cubesats for monitoring atmospheric processes (CubeMAP): a constellation mission to study the middle atmosphere}. Sensors, Systems, and Next-Generation Satellites XXIV. Anais...SPIE, 2020.

\bibitem{b43} \textbf{XPE - Power Estimator}. 2019. Disponível em: $<$https://www.amd.com/en/products/adaptive-socs-and-fpgas/technologies/power-efficiency/power-estimator.html$>$. Acesso em: 28 out. 2024.

\bibitem{b52} ZHOU, Q. et al. \textbf{Design of a compact and reconfigurable onboard data handling system}. 2018 IEEE Intl Conf on Parallel \& Distributed Processing with Applications, Ubiquitous Computing \& Communications, Big Data \& Cloud Computing, Social Computing \& Networking, Sustainable Computing \& Communications (ISPA/IUCC/BDCloud/SocialCom/SustainCom). Anais...IEEE, 2018.



\end{thebibliography}
\end{flushleft}

